---
title: "Final Project"
author: "Cintia Anna Nagy"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import packages

```{r, message = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidyverse)
library(gtools)
library(psych)
library(corrplot)
library(jtools)
library(echoice2)
library(lme4)
library(broom)
library(performance)
library(sjPlot)
library(nortest)

theme_set(theme_apa())
```

# Load data

```{r, message = FALSE}
raw_data <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')
```

# Exploratory data analysis
## Checking the structure and coding errors
   
```{r}
View(raw_data)
```

```{r}
glimpse(raw_data)
```

```{r}
summary(raw_data)
```
```{r}
sum(is.na(raw_data))
```
```{r}
data_clean <- raw_data
```

```{r}
data_clean$imdb <- as.numeric(data_clean$imdb)
```

```{r}
data_clean <- data_clean %>% 
  mutate(date_aired = as.POSIXct(date_aired, format="%Y-%m-%d"))
```

```{r}
sum(is.na(data_clean))
```

```{r}
data_clean <- data_clean %>% 
  drop_na()
```

```{r}
data_clean %>% 
  mutate(year = format(date_aired, format = "Y%"))
```

## Number of episodes per year

```{r}
data_clean <- data_clean %>% 
  mutate(year = format(date_aired, format = "%Y")) %>% 
  mutate(year = as.numeric(year))

ggplot(data_clean, aes(x = year)) +
  geom_histogram() +
  labs(x = "Year",
       y = "Number of episode",
       title = "Episodes per year")
```

## Ratings per year

```{r}
ggplot(data_clean, aes(x = year, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm")
  labs(x = "Year",
       y = "Rating",
       title = "Rating per year")
```

## Which setting is the most popular?

```{r}
data_clean %>% 
  ggplot(aes(x = setting_terrain, y = imdb)) +
  geom_boxplot() +
  labs(x = "Settings",
       y = "Ratings",
       title = "Popularity of different settings")
```
## What about the famous catchphrases?

```{r}
# convert into numeric variables
data_clean <- data_clean %>% 
  mutate(jeepers = as.numeric(jeepers),
         jinkies = as.numeric(jinkies),
         zoinks = as.numeric(zoinks),
         groovy = as.numeric(groovy),
         scooby_doo_where_are_you = as.numeric(scooby_doo_where_are_you),
         rooby_rooby_roo = as.numeric(rooby_rooby_roo))

# check range
data_clean %>% 
  select(c("jeepers", "jinkies", "zoinks", "groovy", "scooby_doo_where_are_you", "rooby_rooby_roo")) %>%
  na.replace(0) %>% 
  summary()
```

```{r}
data_clean %>% 
  ggplot(aes(x = jeepers, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Times jeepers said",
       y = "Ratings",
       title = "Rating vs jeepers")
```
```{r}
data_clean %>% 
  ggplot(aes(x = jinkies, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Times jinkies said",
       y = "Ratings",
       title = "Rating vs jinkies")

```

```{r}
data_clean %>% 
  ggplot(aes(x = zoinks, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Times zoinks said",
       y = "Ratings",
       title = "Rating vs zoinks")
```
```{r}
data_clean %>% 
  ggplot(aes(x = groovy, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Times groovy said",
       y = "Ratings",
       title = "Rating vs groovy")
```
```{r}
data_clean %>% 
  ggplot(aes(x = scooby_doo_where_are_you, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Times scooby doo where are you said",
       y = "Ratings",
       title = "Rating vs scooby do where are you")
```
```{r}
data_clean %>% 
  ggplot(aes(x = rooby_rooby_roo, y = imdb)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Times rooby rooby roo said",
       y = "Ratings",
       title = "Rating vs rooby rooby roo")
```
## Which monster type is the most popular?

```{r}
data_clean_long <- data_clean %>% 
  separate_rows(monster_type, sep = ",") %>% 
  drop_na()

data_clean_long %>% 
  group_by(monster_type) %>% 
  summarise(mean_rating = mean(imdb)) %>% 
  arrange(desc(mean_rating))
```

## Is popularity influenced by the actions of the characters? (who caught the monster, who was captured by the monster, who unmasked the monster, who ate the snack)

```{r}
data_clean_long <- data_clean_long %>% 
  pivot_longer(cols = c("caught_fred", "caught_daphnie", "caught_velma", "caught_shaggy", "caught_scooby"), names_to = "caught", names_prefix = "caught_", values_to = "caught_value") %>%
  filter(caught_value == "TRUE") %>%
  pivot_longer(cols = c("captured_fred", "captured_daphnie", "captured_velma", "captured_shaggy", "captured_scooby"), names_to = "captured", names_prefix = "captured_", values_to = "captured_value") %>% 
  filter(captured_value == "TRUE") %>%
  pivot_longer(cols = c("unmask_fred", "unmask_daphnie", "unmask_velma", "unmask_shaggy", "unmask_scooby"), names_to = "unmask", names_prefix = "unmask_", values_to = "unmask_value") %>%
  filter(unmask_value == "TRUE") %>%
  pivot_longer(cols = c("snack_fred", "snack_daphnie", "snack_velma", "snack_shaggy", "snack_scooby"), names_to = "snack", names_prefix = "snack_", values_to = "snack_value") %>% 
  filter(snack_value == "TRUE")
```

```{r}
data_clean_long %>% 
  ggplot(aes(x = caught, y = imdb)) +
  geom_boxplot() +
  labs(x = "Who caught the monster?",
       y = "Ratings",
       title = "Rating vs who chaught the monster")
```
```{r}
data_clean_long %>% 
  ggplot(aes(x = captured, y = imdb)) +
  geom_boxplot() +
  labs(x = "Who was captured by the monster?",
       y = "Ratings",
       title = "Rating vs Who was captured by the monster")
```
```{r}
data_clean_long %>% 
  ggplot(aes(x = unmask, y = imdb)) +
  geom_boxplot() +
  labs(x = "Who unmasked by the monster?",
       y = "Ratings",
       title = "Rating vs Who unmasked the monster")
```
```{r}
data_clean_long %>% 
  ggplot(aes(x = snack, y = imdb)) +
  geom_boxplot() +
  labs(x = "Who ate the snack?",
       y = "Ratings",
       title = "Rating vs Who ate the snack")
```
Based on the plots, there is no association between ratings and the actions of the characters.

# Statistical models
## Research question
    Is the higher occurrence of catchphrases (jeepers, jinkies, zoinks, groovy, scooby_doo_where_are_you, rooby_rooby_roo) influences the rating of the episode?
    
## Model building 

```{r}
model_1 <- lm(imdb ~ jeepers + jinkies + zoinks + groovy + scooby_doo_where_are_you + rooby_rooby_roo, data_clean)

summary(model_1)
tab_model(model_1, show.std = TRUE)
check_model(model_1)
```
```{r}
model_2 <- lm(imdb ~ jinkies + rooby_rooby_roo, data_clean)

summary(model_2)
tab_model(model_2, show.std = TRUE)
check_model(model_2)
```

```{r}
AIC_1 <- AIC(model_1)
AIC_2 <- AIC(model_2)
BIC_1 <- BIC(model_1)
BIC_2 <- BIC(model_2)

print(paste("AIC of model_1:", AIC_1))
print(paste("AIC of model_2:", AIC_2))
print(paste("BIC of model_1:", BIC_1))
print(paste("BIC of model_2:", BIC_2))
```
Based on the AIC ans BIC, the model with the best performance is the model_2

## Reporting the final model

```{r}
final_model <- model_2

check_model(final_model)

tab_model(final_model, show.std = TRUE)
```
# Discussion

In the final model the *jinkies* and *rooby-rooby-roo* variables were significant (p < 0.001: the more they occurred in the episode, the lower rating the episode got. However the model only explained 17.3 % from the variance (based on the adjusted R2) and also not all of the assumptions are met (homogeneity of variance, normality of residuals).